\href{https://travis-ci.org/bitcoin/bitcoin}{\tt !\mbox{[}Build Status\mbox{]}(https\+://travis-\/ci.\+org/bitcoin/bitcoin.\+svg?branch=master)}

\href{https://www.bitcoin.org}{\tt https\+://www.\+bitcoin.\+org}

\subsection*{What is Bitcoin? }

Bitcoin is an experimental new digital currency that enables instant payments to anyone, anywhere in the world. Bitcoin uses peer-\/to-\/peer technology to operate with no central authority\+: managing transactions and issuing money are carried out collectively by the network. Bitcoin Core is the name of open source software which enables the use of this currency.

For more information, as well as an immediately useable, binary version of the Bitcoin Core software, see \href{https://www.bitcoin.org/en/download}{\tt https\+://www.\+bitcoin.\+org/en/download}.

\subsection*{License }

Bitcoin Core is released under the terms of the M\+I\+T license. See \mbox{[}C\+O\+P\+Y\+I\+N\+G\mbox{]}(C\+O\+P\+Y\+I\+N\+G) for more information or see \href{http://opensource.org/licenses/MIT}{\tt http\+://opensource.\+org/licenses/\+M\+I\+T}.

\subsection*{Development process }

Developers work in their own trees, then submit pull requests when they think their feature or bug fix is ready.

If it is a simple/trivial/non-\/controversial change, then one of the Bitcoin development team members simply pulls it.

If it is a {\itshape more complicated or potentially controversial} change, then the patch submitter will be asked to start a discussion (if they haven\textquotesingle{}t already) on the \href{http://sourceforge.net/mailarchive/forum.php?forum_name=bitcoin-development}{\tt mailing list}.

The patch will be accepted if there is broad consensus that it is a good thing. Developers should expect to rework and resubmit patches if the code doesn\textquotesingle{}t match the project\textquotesingle{}s coding conventions (see doc/developer-\/notes.md) or are controversial.

The {\ttfamily master} branch is regularly built and tested, but is not guaranteed to be completely stable. \href{https://github.com/bitcoin/bitcoin/tags}{\tt Tags} are created regularly to indicate new official, stable release versions of Bitcoin.

\subsection*{Testing }

Testing and code review is the bottleneck for development; we get more pull requests than we can review and test on short notice. Please be patient and help out by testing other people\textquotesingle{}s pull requests, and remember this is a security-\/critical project where any mistake might cost people lots of money.

\subsubsection*{Automated Testing}

Developers are strongly encouraged to write unit tests for new code, and to submit new unit tests for old code. Unit tests can be compiled and run (assuming they weren\textquotesingle{}t disabled in configure) with\+: {\ttfamily make check}

Every pull request is built for both Windows and Linux on a dedicated server, and unit and sanity tests are automatically run. The binaries produced may be used for manual Q\+A testing — a link to them will appear in a comment on the pull request posted by \href{https://github.com/BitcoinPullTester}{\tt Bitcoin\+Pull\+Tester}. See \href{https://github.com/TheBlueMatt/test-scripts}{\tt https\+://github.\+com/\+The\+Blue\+Matt/test-\/scripts} for the build/test scripts.

\subsubsection*{Manual Quality Assurance (Q\+A) Testing}

Large changes should have a test plan, and should be tested by somebody other than the developer who wrote the code. See \href{https://github.com/bitcoin/QA/}{\tt https\+://github.\+com/bitcoin/\+Q\+A/} for how to create a test plan.

\subsection*{Translations }

Changes to translations as well as new translations can be submitted to \href{https://www.transifex.com/projects/p/bitcoin/}{\tt Bitcoin Core\textquotesingle{}s Transifex page}.

Translations are periodically pulled from Transifex and merged into the git repository. See the translation process for details on how this works.

{\bfseries Important}\+: We do not accept translation changes as Git\+Hub pull requests because the next pull from Transifex would automatically overwrite them again.

Translators should also subscribe to the \href{https://groups.google.com/forum/#!forum/bitcoin-translators}{\tt mailing list}. 